A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 main.tex
fix sentences that end with acroynm

\begin{table}
\centering
\caption{Comparison of AFT Models across all hardware and datasets. \acrshort{aic} and \acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred. Concordance (Conc) is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model. \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model. These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}
\label{tab:aft_summary}
\begin{tabular}{lrrrrrrrr}
\toprule
             & AIC              & BIC & Conc & Test Conc & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull      & $-2.11\cdot10^4$ & $-2.11\cdot10^4$ & 0.84 & 0.83 & 0.00 & 0.01 & 0.00 & 0.00 \\
Log Logistic & $-2.18\cdot10^4$ & $-2.18\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.01 & 0.00 & 0.00 \\
Log Normal   & $-2.25\cdot10^4$ & $-2.25\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.00 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}
\begin{figure*}[tph!]
    \centering
        \includegraphics[width=.49\linewidth]{plots/combined/weibull_qq.pdf}
        \includegraphics[width=.49\linewidth]{plots/combined/log_logistic_qq.pdf}
        \includegraphics[width=.49\linewidth]{plots/combined/log_normal_qq.pdf}
    \caption{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red). The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} $. A model that fits this cubic spline exactly would be a diagonal line at $y=x$. The process of comparing the fitted AFT model to a default cubic spline is called \textit{survival probability calibration} and is discussed in more detail in Section~\ref{best-fit}.}
    \label{fig:qq}
\end{figure*}

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken'').
Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}.
By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken'' in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time.
It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.

>>>>

\begin{table}
\centering
\caption{Comparison of AFT Models across all hardware and datasets. \acrshort{aic}~and~\acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred. Concordance (Conc) is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model. \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model. These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}
\label{tab:aft_summary}
\begin{tabular}{lrrrrrrrr}
\toprule
             & AIC              & BIC & Conc & Test Conc & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull      & $-2.11\cdot10^4$ & $-2.11\cdot10^4$ & 0.84 & 0.83 & 0.00 & 0.01 & 0.00 & 0.00 \\
Log Logistic & $-2.18\cdot10^4$ & $-2.18\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.01 & 0.00 & 0.00 \\
Log Normal   & $-2.25\cdot10^4$ & $-2.25\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.00 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}
\begin{figure*}[tph!]
    \centering
        \includegraphics[width=.49\linewidth]{plots/combined/weibull_qq.pdf}
        \includegraphics[width=.49\linewidth]{plots/combined/log_logistic_qq.pdf}
        \includegraphics[width=.49\linewidth]{plots/combined/log_normal_qq.pdf}
    \caption{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red). The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} $. A model that fits this cubic spline exactly would be a diagonal line at $y=x$. The process of comparing the fitted AFT model to a default cubic spline is called \textit{survival probability calibration} and is discussed in more detail in Section~\ref{best-fit}.}
    \label{fig:qq}
\end{figure*}

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken'').
Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}.
By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}.
If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken'' in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}.
Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time.
It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR\@.
